Visual style guide

### 2023-09-09 notebook/results-funding.qmd
Use Libre Franklin

```{r plot-h4c-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h4c_mms <- h4c_mms %>%
  ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(3, 6, 5)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h4c_mms

@@

p_h4c_amces <- h4c_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_funding_short,
    delim = " - ", 
    names = c("feat_funding_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_funding_short = factor(feat_funding_short, levels = levels(h4c_mms$feat_funding_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h4c_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(3, 6, 5)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

>>>>

```{r plot-h4c-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h4c_mms <- h4c_mms %>%
  ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(3, 6, 5)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Libre Franklin",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h4c_mms

@@

p_h4c_amces <- h4c_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_funding_short,
    delim = " - ", 
    names = c("feat_funding_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_funding_short = factor(feat_funding_short, levels = levels(h4c_mms$feat_funding_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h4c_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_funding_short, fill = feat_funding_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(3, 6, 5)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Libre Franklin",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

### 2023-09-09 notebook/results-practices.qmd
Use Libre Franklin

```{r plot-h5c-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h5c_mms <- h5c_mms %>%
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short),
    ncol = 3,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h5c_mms

@@

p_h5c_amces <- h5c_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5c_mms$feat_transp_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5c_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short),
    ncol = 3,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

@@

```{r plot-h5d-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h5d_mms <- h5d_mms %>%
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h5d_mms

@@

p_h5d_amces <- h5d_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5d_mms$feat_transp_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5d_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

@@

```{r plot-h5e-mm-amce, fig.width=14, fig.height=6.5, out.width="100%"}
#| column: page
p_h5e_mms <- h5e_mms %>%
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short, feat_issue),
    ncol = 12,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h5e_mms

@@

p_h5e_amces <- h5e_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5e_mms$feat_transp_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5e_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short, feat_issue),
    ncol = 12,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Clear Sans",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

>>>>

```{r plot-h5c-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h5c_mms <- h5c_mms %>%
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short),
    ncol = 3,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Libre Franklin",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h5c_mms

@@

p_h5c_amces <- h5c_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5c_mms$feat_transp_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5c_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short),
    ncol = 3,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Libre Franklin",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

@@

```{r plot-h5d-mm-amce, fig.width=10, fig.height=6.5, out.width="100%"}
#| column: body-outset-right
p_h5d_mms <- h5d_mms %>%
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Libre Franklin",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h5d_mms

@@

p_h5d_amces <- h5d_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5d_mms$feat_transp_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5d_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_issue),
    ncol = 4,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Libre Franklin",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

@@

```{r plot-h5e-mm-amce, fig.width=14, fig.height=6.5, out.width="100%"}
#| column: page
p_h5e_mms <- h5e_mms %>%
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0.25, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_percent()) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short, feat_issue),
    ncol = 12,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Libre Franklin",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Overall average predicted probability",
    y = NULL,
    fill = NULL,
    title = "Estimated marginal means"
  ) +
  theme(
    legend.position = "top",
    legend.justification = "left",
    legend.margin = margin(l = -7, t = 0)
  )
p_h5e_mms

@@

p_h5e_amces <- h5e_amces %>% 
  ungroup() %>% 
  separate_wider_delim(
    feat_transp_short,
    delim = " - ", 
    names = c("feat_transp_short", "reference_level")
  ) %>% 
  bind_rows(baselines) %>% 
  mutate(feat_transp_short = factor(feat_transp_short, levels = levels(h5e_mms$feat_transp_short))) %>% 
  mutate(feat_govt = factor(feat_govt, levels = levels(h5e_mms$feat_govt))) %>% 
  ggplot(aes(x = avg, y = feat_transp_short, fill = feat_transp_short)) +
  stat_halfeye() +
  geom_vline(xintercept = 0, color = clrs$prism[8], linetype = "dashed", linewidth = 0.25) +
  scale_x_continuous(labels = label_pp) +
  scale_y_discrete(labels = label_wrap(11)) +
  scale_fill_manual(values = clrs$prism[c(10, 3)], guide = "none") +
  facet_nested_wrap(
    vars(feat_govt, feat_funding_short, feat_issue),
    ncol = 12,
    strip = strip_nested(
      text_x = list(element_text(
        family = "Libre Franklin",
        face = "bold"
      ), NULL),
      background_x = list(element_rect(fill = "grey96"), NULL),
      by_layer_x = TRUE
    )
  ) +
  labs(
    x = "Percentage point change in probability of choice selection",
    y = NULL,
    fill = NULL,
    title = "Difference in estimated marginal means"
  )

### 2023-09-09 notebook/style-guide.qmd
Use Libre Franklin

```{scss echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Inter&display=swap');

@@

.inter {
  font-family: "Inter";
}

@@

We use [Inter](https://rsms.me/inter/) (accessible for free from [Google Fonts](https://fonts.google.com/specimen/Inter)) as the main font in all our plots.

::: {.font-example .inter}
**Inter**

>>>>

```{scss echo=FALSE}
@import url('https://fonts.googleapis.com/css2?family=Libre+Franklin&display=swap');

@@

.libre-franklin {
  font-family: "Libre Franklin";
}

@@

We use [Libre Franklin](https://github.com/impallari/Libre-Franklin) (accessible for free from [Google Fonts](https://fonts.google.com/specimen/Libre+Franklin)) as the main font in all our plots.

::: {.font-example .libre-franklin}
**Libre Franklin**
